Mergeable Types

### 2017-02-28 paper/intro.tex

In this paper, we consider how declarative abstractions can be used to
overcome this tension to provide the best of both worlds: functional
programs whose logical structure can be seamlessly transplanted to a
distributed setting, while nonetheless being resilient to system
realities such as network failure and latency.  Our key insight is the
development of a principled methodology that allows us to transform
low-level operational details such as replication and consistency into
high-level compositional abstractions over language-level datatypes.

>>>>

In this paper, we consider how declarative abstractions can be used to
overcome this tension to provide the best of both worlds: functional
programs whose logical structure can be seamlessly transplanted to a
distributed setting, while nonetheless being resilient to system
realities such as network failure and latency.  Our key insight is the
development of a principled methodology that allows us to transform
low-level operational details such as replication and consistency into
high-level compositional abstractions over language-level data types.

### 2017-02-28 paper/model.tex

\name requires a three-way \C{merge} function to merge concurrent
versions of a drawing canvas (see Fig.~\ref{fig:merge-canvas}) that
includes includes two concurrent versions (\C{v1} and \C{v2}),
and their lowest common ancestor (\C{lca}) - the version from which the
two concurrent versions evolved independently. The merge function can
make use of the pixel values of the common ancestor to merge the pixel
values on both the canvases. For instance, if the color of a pixel in
\C{v1} is white, and in \C{v2} it is green, and its color in \C{lca}
is white, then it means that only \C{v2} modified the color. Hence the
pixel is colored green in the merged canvas. On the other hand, if the
pixel is red in \C{v1}, then it means that both \C{v1} and \C{v2} have
modified the color. In such case, an appropriate color-mixing algorithm
can be used to determine the color of pixel.  For instance, the pixel
can be colored yellow - an additive combination of red and green. The
logic is illustrated in Fig.~\ref{fig:canvas-merging}.
\begin{figure}
\begin{center}
  \begin{ocaml}
let color_mix px1 px2 : pixel =
let f = Char.code in
let h x y = Char.chr @@ (x + y)/ 2 in
let (r1,g1,b1) = (f px1.r, f px1.g, f px1.b) in
let (r2,g2,b2) = (f px2.r, f px2.g, f px2.b) in
let (r,g,b) = (h r1 r2, h g1 g2, h b1 b2) in {r=r; g=g; b=b}

>>>>

\name requires a three-way \C{merge} function to merge concurrent
versions of a drawing canvas (see Fig.~\ref{fig:merge-canvas}) that
includes two concurrent versions (\C{v1} and \C{v2}),
and their lowest common ancestor (\C{lca}) - the version from which the
two concurrent versions evolved independently. The merge function can
make use of the pixel values of the common ancestor to merge the pixel
values on both the canvases. For instance, if the color of a pixel in
\C{v1} is white, and in \C{v2} it is green, and its color in \C{lca}
is white, then it means that only \C{v2} modified the color. Hence the
pixel is colored green in the merged canvas. On the other hand, if the
pixel is red in \C{v1}, then it means that both \C{v1} and \C{v2} have
modified the color. In such case, an appropriate color-mixing algorithm
can be used to determine the color of pixel.  For instance, the pixel
can be colored yellow - an additive combination of red and green. The
logic is illustrated in Fig.~\ref{fig:canvas-merging}.
\begin{figure}
\begin{center}
  \begin{ocaml}
let color_mix px1 px2 : pixel =
let f = Char.code in
let h x y = Char.chr @@ (x + y)/ 2 in
let (r1,g1,b1) = (f px1.r, f px1.g, f px1.b) in
let (r2,g2,b2) = (f px2.r, f px2.g, f px2.b) in
let (r,g,b) = (h r1 r2, h g1 g2, h b1 b2) in {r=r; g=g; b=b}
